Parameter estimation

### 2023-08-01 SFE-article/Article_Model_Parameters.tex
01.08

@@

\section{Conclusions} \label{CH: Conclusion}
In this study, a process model was developed by performing parameter estimation using a dataset obtained from experiments conducted at various temperature and pressure levels. The model was found to have good agreement with experimental yield curves for the extraction of caraway oil from caraway seeds. However, it was noticed that the simulation results overshoot the dataset, which may be explained to the presence of losses in the real system, such as some amount of the solute sticking to the inner walls of pipes. Another possible reason could be the need for a more complex mass transfer mechanism than the extraction kinetic presented in this work. For example, the Broken-and-Intact Cell model suggested by \citet{Sovova2017} formulated a general SFE model that includes the solute-matrix interaction. This model allows for solute diffusion from intact cells to the region of broken cells, and the equilibrium is established at the particle surface between the broken cells and fluid phase. Such a mechanism gives more flexibility to the process model to adapt to a dataset.

To establish correlations for the internal and axial diffusion coefficients in terms of fluid density, both linear and non-linear regression techniques were utilized. These correlations facilitated the generalization of the process model to a range of operating conditions, specifically for temperatures ranging from $40^\circ C$ to $50^\circ C$, pressures ranging from 200 bar to 300 bar, and flow rates of 0.4 l/min (with flow variations of up to 5\%). The dependencies given by these correlations can be justified by the influence of the solubility and Graham's Law of Diffusion, as suggested above.

The generalized model can be used to study the impact of different operating conditions on the extraction yield or for economic analysis of the extraction process.

>>>>

\usepackage{placeins}

@@

\section{Conclusions} \label{CH: Conclusion}

This study presented basic aspects regarding the process parameters for obtaining caraway extracts using supercritical $CO_2$ at different operating conditions. A first-principle process model was developed based on governing equations and simplified using the Low-Mach number approximation. The values of unknown parameters in the process model were obtained by parameter estimation. The yield data from the experiments were compared against the yield data generated by the model. The IPOPT solver was used to solve the maximum likelihood estimation. The process model was found to have good agreement with experimental yield curves. Later, the parameters found for each experiment were combined to obtain more general relationships. The correlations for $D_i$, $\Upsilon$ and $D_e^M$ are presented as a function of $\rho$ or $R_e$. It should be noted that obtained correlations have been prepared with a limited amount of data. These correlations can be used to study the impact of different operating conditions on the extraction yield by different methods, such as sensitivity analysis. Moreover, the generalized model could be useful in finding the optimal operating conditions with respect to the process economy.

### 2023-08-01 SFE-article/Sections/Model.tex
01.08

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$. The fluid concentration is assumed to not be uniform, and as such it is described by a function $H=H(z)$. The further discussion on the distribution of concentration in the fluid phase can be found in appendix \ref{CH: IC_BC}. Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$. Therefore, the initial conditions employed in the simulation are:

>>>>

		\subsubsection{Initial and boundary conditions} 
		It is assumed that the solvent is free of solute at the entrance of the extractor and that all the solid particles have the same initial solute content ${\color{magenta}c_{s0}}$. On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase. During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed). As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform. Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory (Figure \ref{fig: estimation_results}). It can be noticed that each curve at the beginning has a curvature, which is not linear. Generally, a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The details on the calculation are given in Appendix \ref{CH: IC_BC}. The linear distribution $H(z)$ can be defined if the total mass of solute $m_{total}$ and initial mass ratio between solid and fluid phases $\tau$ are known.
		Moreover, it is considered that the initial temperature of the extractor in every place is the same and described by ${\color{magenta}h_0}$. Therefore, the initial conditions employed in the simulation are:

### 2023-08-01 SFE-article/Sections/Parameter_estimation.tex
01.08

>>>>

	As a result of fitting, the following parameters are obtained:

	\begin{itemize}
		\item Partition coefficient:\qquad\quad\qquad$k_m$
		\item Internal diffusion coefficient: \quad$D_i^R$
		\item Axial diffusion coefficient: \qquad$D_e^M$
		\item Decay coefficient:\qquad\qquad\qquad$\Upsilon$
		\item Standard deviation:\qquad\qquad\quad~$\sigma^2$
		\item Total mass of solute: \qquad\quad\quad$m_{total}$
		\item Initial mass ratio: \qquad\qquad\qquad$\tau$
	\end{itemize}

	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced. The initial guess for each optimization, the lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}.

 	\begin{table}[h]
		\adjustbox{max width=\columnwidth}{%
			\begin{tabular}{ lccccccc }
				\hline 
				Parameter		&$k_m$[-] 	& $D_i^R$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
				Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
				Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
				Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
		\end{tabular} }
		\caption{Constraints and initial guess}
		\label{tab:Constraints}
	\end{table}

### 2023-08-01 SFE-article/Sections/Results.tex
01.08

    The parameter estimation problem was solved by fitting the process model to the dataset given in the Table \ref{tab: Yield_data}. Each time-series was fitted to the model separately. As a result of fitting, the following parameters were obtained:

    \begin{itemize}
        \item Partition coefficient:\qquad\quad\qquad$k_m$
        \item Internal diffusion coefficient: \quad$D_i$
        \item Axial diffusion coefficient: \qquad$D_e^M$
        \item Decay curvature coefficient:\qquad$\Upsilon$
        \item Standard deviation:\qquad\qquad\quad~$\sigma$
    \end{itemize}

    Moreover, the initial state estimation was performed together with parameter estimation. The initial solute concentration in the solid phase is assumed to be uniformly distributed. On the other hand, the solute concentration in the fluid phase should not follow the same assumption as the solid phase. During the preparation period, the solute diffuses to the fluid phase in contact with the solid particles. Later, the solute in the fluid phase is partially moved along the extractor (if the pressure increase in the system, the pump cause the movement of the fluid, even if the outlet valve is closed). As a result, the distribution of solute mass in the fluid phase is assumed not to be uniform. Some conclusions can be drawn from the analysis of the initial part of each yield curve obtained from the laboratory. It can be noticed that each curve at the beginning has a curvature, which is not linear. Generally, a quadratic function could approximate the initial part of each extraction curve. A function that, after integration, gives a quadratic-like result is a straight line. Based on that observation, the solute concentration in the fluid phase is assumed to be linearly distributed. The solute concentration is assumed to be zero at the outlet and reach the maximum at the beginning of the fixed bed. The details on the calculation are given in appendix \ref{CH: IC_BC}. The linear distribution can be defined if the total mass of solute $m_{total}$ and partition coefficient $\tau$ are known.

    Due to initial state estimation, two additional parameters are fitted.

    \begin{itemize}
        \item Total mass of solute: \qquad\qquad\quad$m_{total}$
        \item Partition coefficient: \qquad\qquad\quad$\tau$
    \end{itemize}

	To ensure that parameters found by the optimizer do not reach unrealistic values, an additional set of inequality constraints is introduced. The lower and upper bounds for each parameter are given in Table \ref{tab:Constraints}. To ensure that the solution is a global solution multiple initial points have been tested but presented results come from the initial guess given also in Table \ref{tab:Constraints}.

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
		\begin{tabular}{ lccccccc }
			\hline 
			Parameter		&$k_m$[-] 	& $D_i$[$m^2/s$] 	& $D_e^M$[$m^2/s$]	& $\Upsilon$ [m$^3$/kg] & $m_{total}$[g]	& $\tau$[-] 	& $\sigma$[-] \\  \hline
			Lower bound		&0	  		& 0 	  			& 0 				&	0					& 80 		 		& 0 	   		& 0 \\ 
			Upper bound		&$+\infty$	& $+\infty$ 		& $+\infty$			&	100					& 150 				& 1 			& $+\infty$ \\ 
			Initial guess	&1e5 		& 3 	  			& 1 				&	0					& 80 		 		& 0.65 	   		& 0.1 \\  \hline
		\end{tabular} }
	\caption{Constraints and initial guess of the parameter estimation problem}
	\label{tab:Constraints}
	\end{table}

%	The parameter estimation problem requires an initial guess as an input to an optimization problem. To ensure that the solution is a global solution multiple initial points have been tested. The initial guesses for the parameter estimation problem are given in Table \ref{tab:InitialGuess}

%	\begin{table}[!h]
%		\centering
%		\adjustbox{max width=\columnwidth}{%
%		\begin{tabular}{ lcccccc } 
%			\hline
%			Parameter		&$k_m$ 	& $D_i$ 	& $D_e^M$ 	& $m_{total}$	& $\tau$ 	& $\sigma$ \\  \hline
%			Initial guess	&1	  	& 3 	  	& 1 		& 77 		 	& 0.65 	   	& 0.1 \\  \hline
%		\end{tabular} }
%		\caption{Constraints of the parameter estimation problem}
%		\label{tab:InitialGuess}
%	\end{table}

	Figure \ref{fig: estimation_results} show yield curves for each of experiments. The blue dots indicate the data point obtained as a measurement from the laboratory experiments. The black curve represents the yield curve obtained from the initial guess of the parameters. The blue curve correspond to yield curve obtained as a solution of the optimization problem. The curves on the left hand-side of the Figure \ref{fig: estimation_results}, are the cumulative yield curves, which represents the cumulative amount of the oil collected during each experiment. The plots on the right hand-side, represent the derivative of the cumulative yield curves. As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\csvautobooktabular{Figures/Results_estimation/estimation.csv} }
		\caption{Parameter estimation results rounded to fifth decimal place}
		\label{tab: Estimation_results}
	\end{table}

	The results of parameter estimation can be found in Table \ref{tab: Estimation_results} and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.

	\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
			\caption{Experiment at $40^\circ C$ and $300$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{\columnwidth}
			\centering
			\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
			\caption{Experiment at $50^\circ C$ and $300$ bar}
		\end{subfigure}
		\caption{Results of parameter estimation}
		\label{fig: estimation_results}
	\end{figure}

	Based on the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors at relatively high. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of the concentration gradient

@@

	Values of the internal diffusion coefficients are distinguished for each experiment. The order of magnitude of $D_i$ obtained from the optimization is similar to values found by other researchers. \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported $D_i \approx 6e-13$. The $\gamma$ (Equation \ref{EQ: C_sat_function}) coefficient multiply the reference value of $D_i$ to take into consideration that solute inside of a particle is harder to obtain than the solute close to the outer surface, as explained before. The curvature of the $\gamma$ function is described by a $\Upsilon$. The higher the value of $D_i \times \gamma$, the higher

	It can be observed that the obtained values of $D_i$ increase as the density increase. This behaviour can be explained by an increase in solubility when the density grow. \citet{Shojaie2010}, proved that the carvone (which is one of the main components of caraway oil) solubility increase together with pressure increase and decrease when temperature increase. $D_i$ and $\Upsilon$ can be related directly to

		\begin{figure*}[!h]
		\centering
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 10.5cm 14cm 10cm 1.5cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Experiment at $40^\circ C$ and $200$ bar}
		\end{subfigure}
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3cm 8cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Experiment at $50^\circ C$ and $200$ bar}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\includegraphics[trim = 2cm 0.4cm 2cm 0.9cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
			\caption{The dependence of the internal diffusion coefficient on the solutes concentration in the solid phase}
			\label{fig:Di_upsilon_res}
		\end{subfigure}
		\caption{Results of parameter estimation}
		%\label{fig: estimation_results}
	\end{figure*}

	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity as a function of the solute's concentration in the solid phase.

	The axial diffusion coefficient obtained from the optimizer seems to be quite high if compared to the internal diffusion coefficients. Nevertheless, the values of $D_e^M$ have similar order of magnitude as reported in literature, for example \citet{ReisVasco2000}. The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments.

@@

	As explained above, and in Appendix \ref{CH: IC_BC}, the linear distribution of can be fully determined if the parameter $\tau$ is known. The split ratio for experiments conducted at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar are similar to each other and close to 0.65. The experiments performed at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have $\tau$ equals to $0.70$ and $0.75$, respectively.

	The noise present in each dataset is quantified by parameter $\sigma$. It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $50 ^\circ C$ / 200 bar have similar value of $\sigma\approx0.36$. The visual investigation of the datasets obtained at $40 ^\circ C$ / 300 bar and $50 ^\circ C$ / 300 bar allow to explain higher values of $\sigma$ for both dataset. Both datasets have higher deviation of the data points from the simulated curve.

	The results obtained from the parameter estimation are used to develop a generalized process model. The model generalization is performed by introducing correlations which link the estimated parameters and the operating conditions. Since the experiments were performed under varying temperature and pressure, the influence of these variables is taken into account. To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure. Since the optimizer found that $k_m$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.

	The other two parameters ($D_i$ and $D_e^M$) are subject to regression to obtain correlations in terms of density. Figure \ref{fig:Regression} shows the first- and second-order polynomials used to fit $D_i$ and $D_e^M$ as a function of fluid density.

%	\begin{figure}[!h]
%		\centering
%		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
%		\caption{Second-order polynomial regression of fitted parameters ($D_i$ and $D_e^M$) as a function of fluid density $\rho_f$}
%		\label{fig:Regression_2}
%	\end{figure}

>>>>

    The parameter estimation problem was solved by fitting the process model to the dataset given in the Figure \ref{fig: estimation_results}. Each time-series present was fitted to the model separately. The blue dots indicate the data point obtained as a measurement from the laboratory experiments. The black curve represents the yield curve obtained from the initial guess of the parameters. The red curve correspond to yield curve obtained as a solution of the optimization problem. Every sub-figure is made of two figure of which one represent the cumulative yield, and the second one shows the derivative of the cumulative yield. As explained in the Chapter \ref{CH: Parameter_estimation}, the derivatives of the cumulative measurements are independent on the previous measurement and should be used for the parameter estimation.
    The parameters obtained from solving the optimization problem can be found in Table \ref{tab: Estimation_results}.

    \begin{figure*}[!h]
    	\centering
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P200.pdf}
    		\caption{Experiment at $40^\circ C$ and $200$ bar}
    	\end{subfigure}
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P200.pdf}
    		\caption{Experiment at $50^\circ C$ and $200$ bar}
    	\end{subfigure}
    	\hfill
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T40_P300_org.pdf}
    		\caption{Experiment at $40^\circ C$ and $300$ bar}
    	\end{subfigure}
    	\begin{subfigure}[b]{\columnwidth}
    		\centering
    		\includegraphics[trim = 2cm 10.5cm 2.5cm 2.02cm,clip,width=\textwidth]{/Results_estimation/Fitting_LUKE_T50_P300_org.pdf}
    		\caption{Experiment at $50^\circ C$ and $300$ bar}
    	\end{subfigure}
    	\caption{Results of parameter estimation}
    	\label{fig: estimation_results}
    \end{figure*}

	 %and the concentration profiles, which correspond for the optimized solution for each experiments, are presented on Figure \ref{fig: estimation_results_profiles} in Appendix \ref{CH: Profiles}.

	\begin{table}[!h]
		\centering
		\adjustbox{max width=\columnwidth}{%
			\csvautobooktabular{Figures/Results_estimation/estimation_2.csv} }
		\caption{Parameter estimation results rounded to fifth decimal place}
		\label{tab: Estimation_results}
	\end{table}

	As shown in the Table \ref{tab: Estimation_results}, the optimizer found optimal values of the partition factors ${\color{orange}k_m}$ at relatively high levels. Such a behaviour suggest that the solvent is far from the saturation, and the model can be simplified. The model reduction can be introduced by considering the limit of the concentration gradient

@@

	Values of the internal diffusion coefficients are distinguished for each experiment. The order of magnitude of ${\color{orange}D_i^R}$ obtained from the optimization is similar to values found by other researchers. \citet{Reverchon1996} performed the parameter estimation for the extraction process of sage oil from seeds and reported ${\color{magenta}D_i^R} \approx 6\times 10^{-13}[m^2/s]$. Figure \ref{fig: results_DI} represent the ${\color{orange}D_i^R}$ as the function of density. As the internal diffusion coefficient describes the diffusion inside of a particle, it is independent of external factors such as a fluid velocity around that particle. In such a case, the internal diffusion depends only on local conditions given by temperature and pressure, which defines the physical properties of a stagnant fluid inside of pores of a particle—considering that the internal diffusion can be represented as a function of the density of the fluid, which is uniquely defined at a given temperature and pressure in the one-phase region. The linear trend in Figure \ref{fig: results_DI} suggests that ${\color{orange}D_i^R}$ increases with fluid density.

	Similarly to the internal diffusion coefficient, the obtained values ${\color{orange}\Upsilon}$ can be represented as a function of the local operating conditions, or by uniquely defined physical properties such as density. Figure \ref{fig: results_upsilon} shows that of ${\color{orange}\Upsilon}$ grows with density. This can be explained if the solubility increases as the density grows. \citet{Shojaie2010}, showed that the solubility of carvone (one of the main components of caraway oil) rises together with pressure increase and decreases when temperature increases.

	The Figure \ref{fig:Di_upsilon_res} shows how the internal diffusivity ${\color{orange}D_i}$ (Equation \ref{EQ: C_sat_function}) as a function of the solute concentration in the solid phase at different operating conditions. The higher the density, the higher solubility according to \citet{Shojaie2010}, which results in higher values of the internal diffusion coefficient and larger curvature of ${\color{orange}D_i}$ function.

		\begin{figure}[!h]
		\centering
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 10.5cm 14cm 10cm 1.5cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Dependency of ${\color{orange}D_i}$}
			\label{fig: results_DI}
		\end{subfigure}
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 3cm 8cm 17.7cm 7.7cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
			\caption{Dependency of ${\color{orange}\Upsilon}$}
			\label{fig: results_upsilon}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.49\columnwidth}
			\includegraphics[trim = 1.0cm 0cm 3cm 0cm, clip, width=\columnwidth]{/Results_estimation/D_i_Uppsilon_results.pdf}
			\caption{Dependency of ${\color{orange}D^R_i}$}
			\label{fig:Di_upsilon_res}
		\end{subfigure}
		\begin{subfigure}[b]{0.49\columnwidth}
			\centering
			\includegraphics[trim = 19.0cm 13.8cm 3.5cm 1.0cm,clip,width=\columnwidth]{/Results_estimation/Trend_Lines_D_e.pdf}
			\caption{Dependency of ${\color{orange}D^M_e}$}
			\label{fig: results_De}
		\end{subfigure}
		\caption{Results of parameter estimation}
		\label{fig: estimation_results_DI_GAMMA}
	\end{figure}

	The axial diffusion coefficient obtained from the optimizer seems is relatively high if compared to the internal diffusion coefficients. The values of ${\color{orange}D_e^M}$ have similar order of magnitude as reported in literature( \citet{ReisVasco2000}). %The relatively high values of the axial diffusion coefficients might be justified by taking into account low values of flow rate used in all the experiments. 
	The axial diffusion can be further analysed by defining the Pecelt number (${\color{orange}P_e} = v \times {\color{magenta}d_p} / {\color{orange}D_e^M} $) and the Reynolds number (${\color{orange}R_e} = v \times {\color{magenta}d_p} / {\color{orange}\mu} $), where ${\color{magenta}d_p}=0.15~[m]$ is the characteristic dimension defined to be the extractor diameter and $\mu$ is the fluid viscosity. %The obtained Pecelt numbers have the order of magnitude of $1 \times 10^{8}$, which suggest that diffusion is negligible, and advection dominates mass transport. 
	The obtained Pecelt numbers are $P_e \gg 1$, which suggest that mass diffusion is negligible, and advection dominates mass transport. An idea to consider a relationship between the Peclet (indirectly the mass diffusion coefficient) and Reynolds numbers has been proposed by \citet{Chung1968}. 
	The Figure \ref{fig: results_De} shows that the obtained values of the mass diffusion coefficient increase almost linearly with increment of the Reynolds number.

@@

	The inital state estimation resulted in values of $\tau$ in range from 0.69 to 0.76. These values are relatively similar to each other. It can be concluded that in the used experimental set-up around 30\% of the solute was extracted to the fluid phase during the preparation period.

	The noise present in each dataset is quantified by parameter $\sigma^2$. It can be observed dataset obtained at $40 ^\circ C$ / 200 bar and $30 ^\circ C$ / 300 bar have similar value of $\sigma^2\approx0.07$. The slightly better results were obtained for the experiment at $50 ^\circ C$ / 300 bar, when $\sigma^2\approx0.05$. The most noisy dataset corresponds to $50 ^\circ C$ / 200 bar, when $\sigma^2\approx0.12$. All values of $\sigma^2$ are relatively low, which suggest the mathematical model is capable to mimic the physical system up to the noise coming from the experiment.

	%The results obtained from the parameter estimation are used to develop a generalized process model. The model generalization is performed by introducing correlations which link the estimated parameters and the operating conditions. Since the experiments were performed under varying temperature and pressure, the influence of these variables is taken into account. To simplify the problem, the correlations are written as functions of fluid density rather than temperature and pressure. Since the optimizer found that ${\color{orange}k_m}$, $m_{total}$ and $C_{lim}$ don't change with the density variations, they are assumed to be constants and not considered further.

%	\begin{figure}[!h]
%		\centering
%		\includegraphics[trim = 11.7cm 14cm 2.3cm 1cm,clip,width=\textwidth]{/Results_estimation/Trend_Lines_order_1.pdf}
%		\caption{Second-order polynomial regression of fitted parameters (${\color{orange}D_i^R}$ and ${\color{orange}D_e^M}$) as a function of fluid density $\rho_f$}
%		\label{fig:Regression_2}
%	\end{figure}

### 2023-08-01 SFE-article/Sections/Saturation.tex
01.08

	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the coefficient ${\color{orange} \gamma}$ is introduced to limit the available oil. The ${\color{orange} \gamma}({\color{blue} c_s} (t,z))$ describes the decay function, which is equal to unity and slowly decays when the amount of the solute in the solid phase decrease. Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact. The ${\color{orange} \gamma}$ parameter multiply the internal diffusion term to indicate that the diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface.

	{\footnotesize
		\begin{equation}
			{\color{orange} \gamma}({\color{blue} c_s} (t,z)) = \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
		\end{equation} }

@@

	{\scriptsize
		\begin{equation}
			\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
		\end{equation} }

>>>>

	Following the idea of the Broken-and-Intact Cell (BIC) model presented by \citet{Sovova2017}, the internal diffusion coefficient ${\color{orange}D_i}$ is consider to be a product of the reference value of ${\color{orange}D_i^R}$ and the exponential decay function ${\color{orange} \gamma}$, as given by Equation \ref{EQ: C_sat_function}.

	{\footnotesize
		\begin{equation}
			{\color{orange}D_i} = {\color{orange}D_i^R} {\color{orange} \gamma}({\color{blue} c_s} (t,z)) = {\color{orange}D_i^R} \exp\left( {\color{magenta}\Upsilon} \left( 1-\cfrac{{\color{blue} c_s} (t,z) }{{\color{magenta}c_{s0}}} \right) \right) \label{EQ: C_sat_function}
		\end{equation} }

@@

	{\scriptsize
		\begin{equation}
			\label{Model_kinetic}
				{\color{blue}r_e}(t,z) = -\cfrac{{\color{orange}D_i^R}({\color{blue}T}(t,z), {\color{red}P}(t)) {\color{orange} \gamma}({\color{blue} c_s} (t,z)) }{{\color{magenta} \mu l^2} } \left({\color{blue}{\color{blue} c_s} }(t,z)  - \cfrac{{\color{magenta}\rho_s}}{{\color{orange}k_m}({\color{blue}T}(t,z)){\color{orange}\rho}({\color{blue}T}(t,z),{\color{red}P}(t))}  {\color{blue}c_f}(t,z) \right)
		\end{equation} }

	Such a formulation limits the availability of the solute in the solid phase. Similarly to the BIC model, this can be explained if oil is assumed to be contained in the cells, a part of which is open because the cell walls were broken by grinding, and the rest remains intact. The diffusion of the solute from a particle's core takes more time compared to the diffusion of the solute located close to the outer surface, considering that the internal diffusion coefficient decay as the concentration of the solute in the solid decrease. As the value of the ${\color{blue}c_s}$ decrease over time, the exponential term approach unity and $\lim_{ {\color{blue}c_s} \rightarrow 0} {\color{orange}D_i} =  {\color{orange}D_i^R}$. ${\color{orange}D_i^R}$ can be interpreted as the internal diffusion coefficient at vanishing gradient.

### 2023-08-01 SFE-article/Sections/Thermo_imp.tex
01.08

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{The compressibility factor}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{The density}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{The specific heat}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
			\caption{The enthalpy}
			\label{fig: SFE_Properties_h}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
			\caption{Viscosity}
			\label{fig: SFE_Properties_Viscosity}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 2.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity}
			\label{fig: SFE_Properties_Thermal}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state and correlations}
		\label{fig: SFE_Properties}
	\end{figure*}

>>>>

	\begin{figure*}[H]
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Compressibility.pdf}	
			\caption{Compressibility factor}
			\label{fig: SFE_Properties_Compressibility}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/RHO.pdf}	
			\caption{Density}
			\label{fig: SFE_Properties_Density}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/CP.pdf}	
			\caption{Specific heat}
			\label{fig: SFE_Properties_CP}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/Enthalpy.pdf}	
			\caption{Enthalpy}
			\label{fig: SFE_Properties_h}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/MU.pdf}
			\caption{Viscosity}
			\label{fig: SFE_Properties_Viscosity}
		\end{subfigure}
		\hfill
		\begin{subfigure}[b]{0.32\textwidth}
			\centering
			\includegraphics[trim = 3.5cm 0cm 1.5cm 0cm,clip,width=\textwidth]{Figures/KT.pdf}	
			\caption{Thermal conductivity}
			\label{fig: SFE_Properties_Thermal}
		\end{subfigure}
		\caption{Properties of $CO_2$ based on the equation of state and correlations}
		\label{fig: SFE_Properties}
	\end{figure*}
